Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression

### 2024-12-03 paper/paper.qmd
styler applied for formatting, and proposed data collection budget added
styler applied for formatting, and proposed data collection budget added

@@

#Display the dataset.
start |>
  tail() |>
  kable(booktabs = TRUE, align = "c")
```

@@

#Calculate the summary of each variable.
count_min <- min(start$count)
count_1st_qu <- quantile(start$count, 0.25)
count_median <- median(start$count)
count_mean <- mean(start$count)
count_3rd_qu <- quantile(start$count, 0.75)
count_max <- max(start$count)

summ <- data_frame(station_name = c("Type: Character", "Number of Unique Values: 27", " ", " ", " ", " "),
                   time = c("Type: Character", "Earliest: 2017-01-01 04:00:00", "Latest: 2024-09-30 20:00:00", " ", " ", " "),
                   count = c(paste("min:",count_min),
                             paste("1st Qu:",count_1st_qu),
                             paste("median:",count_median),
                             paste("mean:", round(count_mean,0)),
                             paste("3rd Qu:",count_3rd_qu),
                             paste("max:",count_max)))

kable(summ)

```

@@

#Calculate the slope.
lm_model <- lm(total_count ~ time, data = daily_counts)
slope <- coef(lm_model)["time"]

ggplot(data = daily_counts, aes(x = time, y = total_count)) +
  geom_point() +
  labs(x = "Time", y = "Daily usage") +
  theme_minimal() +
  geom_smooth(method = "lm") +
  annotate("text", x = max(daily_counts$time), y = max(daily_counts$total_count), 
           label = paste("Slope =", round(slope, 2)), hjust = 1.3)

```

@@

#Calculate the proportion.
total_counts <- start_astime %>%
  group_by(time_interval) %>%
  summarise(count = sum(count, na.rm = TRUE)) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")),
            vjust = -0.5, size = 3) +
  labs(x = "Time interval", y = "Total usage") +
  scale_y_continuous(labels = scales::comma) + 
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 10, hjust = 1)
  )

```

@@

# Handle non-positive integer mean.
merged_data <- merged_data %>%
  mutate(count_difference = ifelse((average_count.y - average_count.x) >= 0, 
                                   ceiling(average_count.y - average_count.x), 
                                   floor(average_count.y - average_count.x)))

ggplot(merged_data, aes(x = station_name, y = count_difference)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
       x = "Station Name",
       y = "Parking volume minus departure volume")+
  ylim(-4, 3)+
  coord_flip()
```

@@

```{r, fig.pos="H"}
#| label: fig-PPvsFV
#| fig-cap: "Pearson Residuals vs Fitted Values for \"Galbraith Rd / King's College Rd\" Model"
#| echo: false
#| message: false
#| warning: false
options(scipen = 999)
poisson_glm <- readRDS(here::here("models/College_St___Huron_St.rds"))
data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>% filter(station_name == "Galbraith Rd / King's College Rd
")%>%
    mutate(
      hour = hour(time),
      day = day(time),
      month = month(time),
      year = year(time)
    )

@@

# Plot residuals vs fitted values
ggplot(data, aes(x = fitted(poisson_glm), y = pearson_residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(x = "Fitted Values", y = "Pearson Residuals")

```
@fig-PPplot is the posterior predictive check plot of the model of the "Galbraith Rd / King's College Rd" station. The posterior predictive check plot highlights several strengths of the model. The predicted distribution ($y_{rep}$) closely aligns with the observed distribution ($y$), particularly at the primary density peak near 0 and the secondary peaks within the 2-5 range, indicating that the model effectively captures the overall data distribution. Additionally, the model successfully reflects the multimodal nature of the data, accurately identifying multiple peaks, which demonstrates its capability to handle complex data patterns. The tail behavior of the predicted distribution is also consistent with the observed distribution, showing that the model performs well in accounting for rare or extreme events. Furthermore, the uncertainty of the predicted distribution is appropriately moderate, neither too narrow to indicate overconfidence nor too wide to suggest excessive variability.

@@

# Display as a table
kable(credible_intervals_df, format = "html", digits = 2, align = "c",
      col.names = c("2.5%", "97.5%"))
```

@@

# Target stations
ut_stations <- c("Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W", 
                 "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
                 "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
                 "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
                 "Wellesley St W / Queen's Park Cres", "Queen's Park Cres E / Grosvenor St - SMART", 
                 "Bay St / Bloor St W (East Side)", "Bay St / Bloor St W (West Side)", "Bay St / Charles St W - SMART",
                 "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W", 
                 "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
                 "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)")

@@

# Iterate through all models.
for (station in ut_stations) {
  station_data <- subset(start, station_name == station)
  path <- paste(paste0("models/", gsub("[ /]", "_", station), ".rds"))
  md <- readRDS(here::here(path))
  target <- data_frame(
    hour = 4,
    day = 26,
    month = 9,
    year = 2026
  )
  target$predicted <- ceiling(exp(predict(md, newdata = target)))
  target$station_name <- station
  target <- target %>% select(-hour,-day,-month,-year)
  result[result$station_name == station, "prediction"] <- target$predicted
}

@@

# Create the plot
ggplot(data_long, aes(x = station_name, y = value, fill = Note)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7), width = 0.7) +
  geom_text(aes(label = value), 
            position = position_dodge(width = 0.7), 
            vjust = -0.5, 
            size = 3) + 
  labs(
    x = "Station Name",
    y = "Usage",
  ) +
  scale_fill_manual(
    values = c("count" = "pink", "prediction" = "skyblue"),
    labels = c("count" = "Actual usage in 2024", "prediction" = "Predicted usage in 2025") 
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```
The prediction indicates an average increase of 2 uses per station across the 27 shared bike stations between 4:00 AM and 8:00 AM on September 26, 2025, compared to the same period in 2024. Specifically, 8 stations are projected to see an increase of 3 uses, 14 stations an increase of 2 uses, and 3 stations an increase of 1 use. Meanwhile, one station is expected to experience no change, and another is forecasted to see a decrease of 1 use.

@@

This study proposes an ideal data collection approach for bike-sharing systems, emphasizing key aspects like data diversity, reliable data collection, anomaly detection and correction, and ethical considerations.

@@

@@

# Display first table
kable(bike_share_part1)

```

@@

#Simulated Ideal Dataset Part 2.
bike_share_part2 <- data.frame(
  End_Station_ID = sample(100:200, 5, replace = TRUE),
  End_Station_Name = paste("Station", sample(100:200, 5, replace = TRUE)),
  Latitude = round(runif(5, 43.6, 43.7), 6),
  Longitude = round(runif(5, -79.4, -79.3), 6),
  Trip_ID = paste("TRIP", sample(1000:9999, 5, replace = TRUE), sep = "-")
)

# Display second table
kable(bike_share_part2)

```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-p3
#| tbl-cap: "Simulated Ideal Dataset Part 3"
#Simulated Ideal Dataset Part 3.
bike_share_part3 <- data.frame(
  Trip_Duration_s = sample(300:3600, 5, replace = TRUE),
  Trip_Distance_m = sample(500:10000, 5, replace = TRUE),
  Bike_ID = paste("BIKE", sample(1000:9999, 5, replace = TRUE), sep = "-"),
  User_Type = sample(c("Member", "Casual"), 5, replace = TRUE)
)

# Display third table
kable(bike_share_part3)

```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-p4
#| tbl-cap: "Simulated Ideal Dataset Part 4"
#Simulated Ideal Dataset Part 4.
bike_share_part4 <- data.frame(
  Weather_Conditions = sample(c("Sunny", "Cloudy", "Rainy"), 5, replace = TRUE),
  Air_Quality_Index = sample(10:100, 5, replace = TRUE),
  Traffic_Conditions = sample(c("Low", "Moderate", "High"), 5, replace = TRUE),
  Available_Bikes_at_Start_Station = sample(0:20, 5, replace = TRUE)
)

# Display fourth table
kable(bike_share_part4)

```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-p5
#| tbl-cap: "Simulated Ideal Dataset Part 5"
#Simulated Ideal Dataset Part 5.
bike_share_part5 <- data.frame(
  Available_Docks_at_End_Station = sample(0:20, 5, replace = TRUE),
  Device_Status = sample(c("Operational", "Faulty"), 5, replace = TRUE),
  Maintenance_Records = sample(c("None", "Minor Repair", "Major Repair"), 5, replace = TRUE)
)

# Display fifth table
kable(bike_share_part5)

```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-p6
#| tbl-cap: "Simulated Ideal Dataset Part 6"
#Simulated Ideal Dataset Part 6.
bike_share_part6 <- data.frame(
  User_Gender = sample(c("Male", "Female", "Other"), 5, replace = TRUE),
  Anomalies = sample(c("None", "Sensor Error", "Docking Failure"), 5, replace = TRUE),
  Missing_Data_Flag = sample(c(TRUE, FALSE), 5, replace = TRUE),
  Data_Source = sample(c("Station Sensor", "Mobile App", "System Log"), 5, replace = TRUE)
)

# Display sixth table
kable(bike_share_part6)

```

>>>>

**testthat**[@tt]: Used to test whether the simulated data and analysis data meet the expected requirements.

**styler**[@styler]: Used to organize code formatting and code comments.

@@

# Display the dataset.
start |>
  tail() |>
  kable(booktabs = TRUE, align = "c")
```

@@

# Calculate the summary of each variable.
count_min <- min(start$count)
count_1st_qu <- quantile(start$count, 0.25)
count_median <- median(start$count)
count_mean <- mean(start$count)
count_3rd_qu <- quantile(start$count, 0.75)
count_max <- max(start$count)

summ <- data_frame(
  station_name = c("Type: Character", "Number of Unique Values: 27", " ", " ", " ", " "),
  time = c("Type: Character", "Earliest: 2017-01-01 04:00:00", "Latest: 2024-09-30 20:00:00", " ", " ", " "),
  count = c(
    paste("min:", count_min),
    paste("1st Qu:", count_1st_qu),
    paste("median:", count_median),
    paste("mean:", round(count_mean, 0)),
    paste("3rd Qu:", count_3rd_qu),
    paste("max:", count_max)
  )
)

kable(summ)
```

@@

# Calculate the slope.
lm_model <- lm(total_count ~ time, data = daily_counts)
slope <- coef(lm_model)["time"]

ggplot(data = daily_counts, aes(x = time, y = total_count)) +
  geom_point() +
  labs(x = "Time", y = "Daily usage") +
  theme_minimal() +
  geom_smooth(method = "lm") +
  annotate("text",
    x = max(daily_counts$time), y = max(daily_counts$total_count),
    label = paste("Slope =", round(slope, 2)), hjust = 1.3
  )
```

@@

# Calculate the proportion.
total_counts <- start_astime %>%
  group_by(time_interval) %>%
  summarise(count = sum(count, na.rm = TRUE)) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(data = total_counts, aes(x = time_interval, y = count, fill = time_interval)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")),
    vjust = -0.5, size = 3
  ) +
  labs(x = "Time interval", y = "Total usage") +
  scale_y_continuous(labels = scales::comma) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 10, hjust = 1)
  )
```

@@

# Handle non-positive integer mean.
merged_data <- merged_data %>%
  mutate(count_difference = ifelse((average_count.y - average_count.x) >= 0,
    ceiling(average_count.y - average_count.x),
    floor(average_count.y - average_count.x)
  ))

ggplot(merged_data, aes(x = station_name, y = count_difference)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    x = "Station Name",
    y = "Parking volume minus departure volume"
  ) +
  ylim(-4, 3) +
  coord_flip()
```

@@

```{r, fig.pos="H"}
#| label: fig-PPvsFV
#| fig-cap: "Pearson Residuals vs Fitted Values for \"Galbraith Rd / King's College Rd\" Model"
#| echo: false
#| message: false
#| warning: false
options(scipen = 999)
poisson_glm <- readRDS(here::here("models/College_St___Huron_St.rds"))
data <- read_parquet(here::here("data/02-analysis_data/start.parquet")) %>%
  filter(station_name == "Galbraith Rd / King's College Rd
") %>%
  mutate(
    hour = hour(time),
    day = day(time),
    month = month(time),
    year = year(time)
  )

@@

# Plot residuals vs fitted values
ggplot(data, aes(x = fitted(poisson_glm), y = pearson_residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(x = "Fitted Values", y = "Pearson Residuals")
```
@fig-PPplot is the posterior predictive check plot of the model of the "Galbraith Rd / King's College Rd" station. The posterior predictive check plot highlights several strengths of the model. The predicted distribution ($y_{rep}$) closely aligns with the observed distribution ($y$), particularly at the primary density peak near 0 and the secondary peaks within the 2-5 range, indicating that the model effectively captures the overall data distribution. Additionally, the model successfully reflects the multimodal nature of the data, accurately identifying multiple peaks, which demonstrates its capability to handle complex data patterns. The tail behavior of the predicted distribution is also consistent with the observed distribution, showing that the model performs well in accounting for rare or extreme events. Furthermore, the uncertainty of the predicted distribution is appropriately moderate, neither too narrow to indicate overconfidence nor too wide to suggest excessive variability.

@@

# Display as a table
kable(credible_intervals_df,
  format = "html", digits = 2, align = "c",
  col.names = c("2.5%", "97.5%")
)
```

@@

# Target stations
ut_stations <- c(
  "Madison Ave / Bloor St W", "Bloor St W / Huron St", "St. George St / Bloor St W",
  "Sussex Ave / St George St", "Spadina Ave / Sussex Ave", "Spadina Ave / Harbord St - SMART",
  "St. George St / Hoskin Ave", "Spadina Ave / Willcocks St", "St. George St / Willcocks St",
  "Willcocks St / St. George St", "Queen's Park / Bloor St W", "Queen's Park Cres W / Hoskin Ave",
  "Wellesley St W / Queen's Park Cres", "Queen's Park Cres E / Grosvenor St - SMART",
  "Bay St / Bloor St W (East Side)", "Bay St / Bloor St W (West Side)", "Bay St / Charles St W - SMART",
  "St. Joseph St / Bay St - SMART", "Bay St / St. Joseph St", "Bay St / Wellesley St W",
  "Ursula Franklin St / Huron St - SMART", "Ursula Franklin St / St. George St - SMART", "Galbraith Rd / King's College Rd",
  "College St / Huron St", "College St / Henry St ", "Queens Park Cres / College St ", "University Ave / College St (East)"
)

@@

# Iterate through all models.
for (station in ut_stations) {
  station_data <- subset(start, station_name == station)
  path <- paste(paste0("models/", gsub("[ /]", "_", station), ".rds"))
  md <- readRDS(here::here(path))
  target <- data_frame(
    hour = 4,
    day = 26,
    month = 9,
    year = 2026
  )
  target$predicted <- ceiling(exp(predict(md, newdata = target)))
  target$station_name <- station
  target <- target %>% select(-hour, -day, -month, -year)
  result[result$station_name == station, "prediction"] <- target$predicted
}

@@

# Create the plot
ggplot(data_long, aes(x = station_name, y = value, fill = Note)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7), width = 0.7) +
  geom_text(aes(label = value),
    position = position_dodge(width = 0.7),
    vjust = -0.5,
    size = 3
  ) +
  labs(
    x = "Station Name",
    y = "Usage",
  ) +
  scale_fill_manual(
    values = c("count" = "pink", "prediction" = "skyblue"),
    labels = c("count" = "Actual usage in 2024", "prediction" = "Predicted usage in 2025")
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
The prediction indicates an average increase of 2 uses per station across the 27 shared bike stations between 4:00 AM and 8:00 AM on September 26, 2025, compared to the same period in 2024. Specifically, 8 stations are projected to see an increase of 3 uses, 14 stations an increase of 2 uses, and 3 stations an increase of 1 use. Meanwhile, one station is expected to experience no change, and another is forecasted to see a decrease of 1 use.

@@

This study proposes an ideal data collection approach for bike-sharing systems, emphasizing key aspects such as data diversity, reliable data collection, anomaly detection and correction, and ethical considerations. Additionally, the study presents an ideal budget structure, a comprehensive checklist for data collection, and an ideal data framework.

@@

## Proposed Budget Estimation for Data Collection
When planning the budget for data collection in a bike-sharing system, several key components must be considered, including hardware, data storage and processing, software development and maintenance, personnel costs, and third-party services. Below is a detailed budget estimate:

1. **Hardware**
   - **IoT Sensors and GPS Modules:** Each bike requires basic sensors (e.g., accelerometers, GPS modules), costing approximately 50-100 CAD per unit. For a system with 1,000 bikes, the initial investment is estimated at 50,000-100,000 CAD.
   - **Station Sensors and Networking Equipment:** Each station requires sensors, wireless communication modules, and network base stations, with costs ranging from 500-1,000 CAD per station. For 100 stations, this totals 50,000-100,000 CAD.
   - **Renewable Energy Systems (Optional):** Installing solar power systems at stations can cost 1,000-2,000 CAD per unit. For 100 stations, the cost would be 100,000-200,000 CAD.

2. **Data Storage and Processing**
   - **Cloud Storage:** Cloud services for storing and managing data depend on the data volume. Assuming 1GB of data is collected daily (including bike, station, and environmental data), annual storage costs are estimated at 5,000-10,000 CAD.
   - **Data Processing and Analysis:** Cloud computing or local server capabilities for data processing may require an initial setup cost of 10,000-30,000 CAD, with annual operating costs of 10,000-20,000 CAD.

3. **Software Development and Maintenance**
   - **Data Collection and Analysis Platform:** Developing a platform for real-time data collection and analysis can cost 50,000-100,000 CAD initially.
   - **System Maintenance and Updates:** Annual maintenance costs are estimated at 10,000-30,000 CAD, including bug fixes, new feature development, and performance optimization.

4. **Personnel Support**
   - **Technical Team:** A team of five professionals, including data engineers, software developers, and project managers, may have an average annual salary of 60,000-100,000 CAD per person. The annual personnel budget is 300,000-500,000 CAD.
   - **Third-Party Support:** Outsourced services or consultancy support may cost 20,000-50,000 CAD annually.

5. **Third-Party Services**
   - **API Integration:** Subscriptions for weather, traffic congestion, and air quality data APIs typically cost 1,000-5,000 CAD annually. Comprehensive API integration costs can range from 5,000-20,000 CAD annually.
   - **Privacy and Compliance Audits:** Engaging third-party firms to conduct privacy protection and compliance audits costs approximately 10,000-20,000 CAD per audit, with an annual budget of 20,000-50,000 CAD.

6. **Operations and Miscellaneous Costs**
   - **Station Maintenance:** Includes sensor calibration and hardware upkeep, with an annual budget of 20,000-50,000 CAD.
   - **Training Costs:** Training technical and management teams on data platform usage and privacy protocols may require 10,000-20,000 CAD annually.

**Total Budget Estimate**

- **Initial Investment (Hardware and Development):** 200,000-500,000 CAD, depending on system scale.

- **Annual Operating and Maintenance Costs:** 100,000-300,000 CAD, covering personnel, data processing, storage, and hardware upkeep.

This budget estimate is designed for a medium-sized bike-sharing system and may vary depending on the number of bikes, stations, data requirements, and operational scale. Adjustments can be made to fit specific project needs.

@@

# Display first table
kable(bike_share_part1)
```

@@

# Simulated Ideal Dataset Part 2.
bike_share_part2 <- data.frame(
  End_Station_ID = sample(100:200, 5, replace = TRUE),
  End_Station_Name = paste("Station", sample(100:200, 5, replace = TRUE)),
  Latitude = round(runif(5, 43.6, 43.7), 6),
  Longitude = round(runif(5, -79.4, -79.3), 6),
  Trip_ID = paste("TRIP", sample(1000:9999, 5, replace = TRUE), sep = "-")
)

# Display second table
kable(bike_share_part2)
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-p3
#| tbl-cap: "Simulated Ideal Dataset Part 3"
# Simulated Ideal Dataset Part 3.
bike_share_part3 <- data.frame(
  Trip_Duration_s = sample(300:3600, 5, replace = TRUE),
  Trip_Distance_m = sample(500:10000, 5, replace = TRUE),
  Bike_ID = paste("BIKE", sample(1000:9999, 5, replace = TRUE), sep = "-"),
  User_Type = sample(c("Member", "Casual"), 5, replace = TRUE)
)

# Display third table
kable(bike_share_part3)
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-p4
#| tbl-cap: "Simulated Ideal Dataset Part 4"
# Simulated Ideal Dataset Part 4.
bike_share_part4 <- data.frame(
  Weather_Conditions = sample(c("Sunny", "Cloudy", "Rainy"), 5, replace = TRUE),
  Air_Quality_Index = sample(10:100, 5, replace = TRUE),
  Traffic_Conditions = sample(c("Low", "Moderate", "High"), 5, replace = TRUE),
  Available_Bikes_at_Start_Station = sample(0:20, 5, replace = TRUE)
)

# Display fourth table
kable(bike_share_part4)
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-p5
#| tbl-cap: "Simulated Ideal Dataset Part 5"
# Simulated Ideal Dataset Part 5.
bike_share_part5 <- data.frame(
  Available_Docks_at_End_Station = sample(0:20, 5, replace = TRUE),
  Device_Status = sample(c("Operational", "Faulty"), 5, replace = TRUE),
  Maintenance_Records = sample(c("None", "Minor Repair", "Major Repair"), 5, replace = TRUE)
)

# Display fifth table
kable(bike_share_part5)
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-p6
#| tbl-cap: "Simulated Ideal Dataset Part 6"
# Simulated Ideal Dataset Part 6.
bike_share_part6 <- data.frame(
  User_Gender = sample(c("Male", "Female", "Other"), 5, replace = TRUE),
  Anomalies = sample(c("None", "Sensor Error", "Docking Failure"), 5, replace = TRUE),
  Missing_Data_Flag = sample(c(TRUE, FALSE), 5, replace = TRUE),
  Data_Source = sample(c("Station Sensor", "Mobile App", "System Log"), 5, replace = TRUE)
)

# Display sixth table
kable(bike_share_part6)
```
